\documentclass[a4paper]{article}

\usepackage[english]{babel} \usepackage{hyperref} \usepackage{float}
\usepackage[utf8]{inputenc} \usepackage{amsmath} \usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} \usepackage{tikz}
\usepackage{pdfpages} \usepackage{listings}
\usepackage[super]{nth}

\usetikzlibrary{arrows,positioning,shapes.geometric}

\title{ Expansão Exponencial }


\author{\normalsize Schneider\\\normalsize}

\date{\color{black}22 de Março de 2022}

\begin{document} \maketitle

\section{Introduction}
 The format compression zip is used to compress files, images, software, etc, this format was created by Phil Katz that launched in January 1989 the first version of software compression PKZIP.  Zip files are individual files that could contain one or many compress files. A zip file is easy to be shared, transported, sent by e-mail, or downloaded.  7-Zip is open source software and the most of the source code is under the GNU LGPL license, we can use 7-Zip on any computer and is totally free, for this software we have high compression ratio with LZMA and LZMA2, supported formats like 7z, xz, tar, etc to packing and ar, arj, cab, iso to unpacking (Pavlov)
Linux is an operating system that manages all of the hardware resources in a computer, there are different versions like Ubuntu, fedora, back track, etc. Operating systems based in Linux are open source this means that we could do many things with the system, for example we could manage or change the kernel.
The kernel is a program that constitutes the central core of a computer operating system. It has complete control over everything that occurs in the system and is the part of the operating system to load into memory during booting (LinuxFoundation)


\begin{thebibliography}{} 
    
    \bibitem{Pavlov} Pavlov, I.
    (n.d). 7-Zip. Recovered from http://www.7-zip.org/
        
    \bibitem{LinuxFoundation} LinuxFoundation(n.d). What is linux?. Recovered from https://www.linux.com/what-is-linux
        
    \bibitem{Deepack} Deepack, P . What is swappiness and how do we change its value?, Recovered from http://www.golinuxhub.com/2014/01/what-is-swappiness-and-how-do-we-change.html  

    \bibitem{Deepack} Deepack, P . What is swappiness and how do we change its value?, Recovered from http://www.golinuxhub.com/2014/01/what-is-swappiness-and-how-do-we-change.html  


   
\end{thebibliography}

\end{document}